Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-07-22 template.tex
another update ... trying to get energy

The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}. The delayed time is $t_{\rm r} = t-r/c$.  The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.  The value often quoted for the RF bandwidth in ice ($n=1.78$) is 55.8 degrees.  The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta$ is close to $\theta_{\rm C}$.  The $n_{\rm max}$ parameter is the maximum excess negative charge in the cascade, and the overall RF amplitude is propotional to $n_{\rm max} a$.  Hanson and Hartig (HH) have shown that the parameter $p$ is related to the pulse width \cite{PhysRevD.105.123019}:

\begin{equation}
\sigma_t = \sqrt{2p}
\end{equation}

There is a deep connection between $s(t)$, Eqs. \ref{eq:final}-\ref{eq:final2}, and the natural logarithm of the UHE-$\nu$ cascade energy, $\ln(E_{\rm C}/E_{\rm crit})$. The authors of \cite{PhysRevD.105.123019} have shown that
\begin{equation}
a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
\end{equation}
\end{itemize}

>>>>

The time $t$ is the independent variable of the inverse Fourier transform of the equations in \cite{10.1103/physrevd.65.016003}. The delayed time is $t_{\rm r} = t-r/c$.  The Cherenkov angle $\theta_{\rm C}$ is set by the index of refraction, $n$, via $\cos\theta_{\rm C} = 1/n$.  The value for the RF bandwidth in solid ice ($n=1.78$) is 55.8 degrees.  More detail on the index of refraction in polar ice is given in \cite{Barwick:2018497,ALLISON201963}.  The viewing angle $\theta$ is measured relative to the cascade axis, and the Askaryan radiation is concentrated when $\theta \approx \theta_{\rm C}$.  The $n_{\rm max}$ parameter is the maximum excess negative charge in the cascade, and the overall RF amplitude is propotional to $n_{\rm max} a$.  Hanson and Hartig (HH) have shown that the parameter $p$ is related to $\sigma_t$ \cite{PhysRevD.105.123019}:

\begin{equation}
\sigma_t = \sqrt{2p} \label{eq:pulse_width}
\end{equation}

The authors of \cite{PhysRevD.105.123019} have shown that, because $\cos\theta - \cos\theta_{\rm C} \approx -\sin\theta_{\rm C}(\theta-\theta_{\rm C})$ to first order in $\Delta\theta = (=\theta-\theta_{\rm C}$, $p \propto \Delta\theta^2$ to second order, and

\begin{equation}
a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
\end{equation}

Qualitatively, this notion was identified by RB in Sec. III of \cite{10.1103/physrevd.65.016003}.  Discuss error prop to lnE
\end{itemize}
